### 2023-10-12 parallel-computing/main.tex
add(tex): config parallel-computing course

% !TEX program = xelatex
\documentclass[20pt, a4paper]{article}
\usepackage{hyperref}
% Justify paragraphs
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\settextfont[Scale=1]{XB Roya}
\renewcommand{\baselinestretch}{1.5}

\begin{document}
\centerline{الگوریتم‌های موازی}
\centerline{علیرضا سلطانی نشان}
\centerline{\today}
\tableofcontents

\end{document}