### 2023-10-12 advance-os/practices/free_bsd.tex
add: wirte initial practices sections

% !TEX program = xelatex
\documentclass[20pt, a4paper]{article}
\usepackage{hyperref}
% Justify paragraphs
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\settextfont[Scale=1]{XB Roya}
\renewcommand{\baselinestretch}{1.5}

\begin{document}
\centerline{سیستم عامل \lr{Free BSD}}
\centerline{علیرضا سلطانی نشان}
\centerline{\today}

\tableofcontents

\section{توضیح اولیه}

\section{تاریخچه}

\section{ویژگی‌های کلیدی}

\subsection{موارد استفاده}

\subsection{شبکه}

\subsection{حافظه}

\subsection{امنیت}

\end{document}