### 2023-10-17 research-methodology/main.tex
add(course): update table of content

% !TEX program = xelatex
\documentclass[20pt, a4paper]{article}
\usepackage{hyperref}
% Justify paragraphs
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\settextfont[Scale=1]{XB Roya}
\renewcommand{\baselinestretch}{1.5}

\begin{document}
\centerline{روش تحقیق}
\centerline{علیرضا سلطانی نشان}
\centerline{\today}
\tableofcontents

\section{اهمیت تحقیق}

\section{فرایند تحقیق}

\section{سمینار و پروپوزال و پایان‌نامه}

\section{سامانه پژوهشیار}

\section{سرقت علمی}

\section{پایگاه‌های اطلاعاتی}

\section{همایش و مجله}

\section{ارائه علمی}

\end{document}