### 2023-12-30 advance-database/main.tex

\documentclass[a4paper]{article}
\usepackage{float}
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{plantuml}
\usetikzlibrary{arrows, shapes, automata, petri, positioning, calc}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\newgeometry{left=1.4cm, right=1.4cm, bottom=2.0cm, top=2.0cm}
\settextfont[Scale=1]{XB Roya}
\renewcommand{\baselinestretch}{1.5}

\begin{document}
\centerline{پایگاه داده پیشرفته}
\centerline{دکتر شجاعی مهر}
\centerline{علیرضا سلطانی نشان}
\centerline{\today}
\tableofcontents
\newpage
\include{acid}
\include{concurrency}
\include{recoverability}
\include{concurrency_control}
\include{timestamp_protocol}
\include{deadlock}
\include{recoverable_strategies}
\end{document}