### 2024-07-12 requirement-engineering/final/soil_monitoring_system.tex
init final projects

\documentclass[a4paper]{article}
\usepackage{forest}
\usepackage{float}
\usepackage{pgf-pie}
\usepackage{pgfplots} 
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{plantuml}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\usetikzlibrary{shapes, arrows, positioning}
\newgeometry{left=1.4cm, right=1.4cm, bottom=2.0cm, top=2.0cm}
\settextfont[Scale=1]{XB Roya}
\input{../config}

\title{مهندسی نیازمندی‌ها \\ خانم دکتر سپیده آدابی}

\begin{document}
\maketitle

\end{document}