### 2024-09-16 software-test/practices/failure_vs_fault.tex
update: add latest complexity theory and initialize software testing

\documentclass[10pt, a4paper]{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage[sanitizesort=false,sanitize={name=false},nomain,xindy,acronym]{glossaries}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage{algpseudocodex}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\usepackage{multirow}
\usepackage{chngcntr}

\settextfont[Scale=1]{XB Roya}

\title{تفاوت میان \lr{Failure} و \lr{Fault}}
\author{علیرضا سلطانی نشان}

\begin{document}
\maketitle

\newpage
\bibliographystyle{plain-fa}
\bibliography{failure_fault_refs.bib}
\end{document}