### 2024-10-11 system-evaluation/system-evaluation.tex

\documentclass[a4paper]{article}
\usepackage{forest}
\usepackage{float}
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\newgeometry{left=1.4cm, right=1.4cm, bottom=2.0cm, top=2.0cm}
\settextfont[Scale=1]{XB Roya}
\input{config}

\title{ارزیابی کارایی سیستم \\ آقای دکتر مهدی امینیان}
\author{علیرضا سلطانی نشان}

\begin{document}
\maketitle
\tableofcontents

\section*{مجوز}

به فایل license همراه این برگه توجه کنید. این برگه تحت مجوز GPLv3 منتشر شده است
که اجازه نشر و استفاده (کد و خروجی/pdf) را رایگان می‌دهد.

\section*{کتاب مرجع}

مرجع این جزوه تدریسی است که در کلاس صورت گرفته، و تدریس آن برگرفته از منابع زیر
می‌باشد:

\begin{LTR}
    \begin{itemize}
        \item \lr{Kishor S. Trivedi, Probability and Statistics with
        Reliability, Queuing, and Computer Science Applications, John Wiley and
        Sons, New York, 2001.}
        \item \lr{Raj Jain, The Art of Computer Systems Performance Analysis:
        Techniques for Experimental Design, Measurement, Simulation, and
        Modeling, John Wiley and Sons, Inc., New York, NY, 1991.}
        \item \lr{Daniel A. Menasce, Virgilio A.F. Almeida, and Lawrence W.
        Dowdy, Performance by Design: Computer Capacity Planning by Example,
        Prentice Hall, 2004.}
        \item \lr{K. Kant, Introduction to Computer System Performance
        Evaluation, McGraw-Hill Inc., 1992.}
        \item \lr{Nader Nematollahi, Probability \& Statistics for Engineers,
        IUST Press,1382}
        \item \lr{S. Mahmood Mirkhan, Stochastic Process, IAU Press, 1391}
    \end{itemize}
\end{LTR}

\input{chapters/chapter_1.tex}

\end{document}