### 2024-11-01 large_scale/practices/normalization.tex

\documentclass[a4paper]{article}
\usepackage{forest}
\usepackage{float}
\usepackage{makecell}
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\newgeometry{left=1.4cm, right=1.4cm, bottom=2.0cm, top=2.0cm}
\settextfont[Scale=1]{XB Roya}

\title{فرمول نرمالسازی یکا‌ها}
\author{علیرضا سلطانی نشان}

\begin{document}
\maketitle

\newpage
\bibliographystyle{unsrt-fa}
\bibliography{normalization_refs.bib}
\end{document}