### 2024-11-14 large-scale/practices/trx_exceptions.tex

\documentclass[a4paper]{article}
\usepackage{forest}
\usepackage{float}
\usepackage{makecell}
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{xepersian}
\usepackage{subfiles}
\settextfont[Scale=1]{XB Roya}

\title{}
\author{علیرضا سلطانی نشان}

\begin{document}
\maketitle

تمرین: 2phace commit و 3phace commit چیه.

% \bibliographystyle{unsrt-fa}
% \bibliography{normalization_refs.bib}
\end{document}