### 2024-11-16 large-scale/draft.tex
update: complete session 6

% transactions

% بحثی وجود داره که مسابقه بر سر منابع. که این تاکتیه که تمرینه این مشکل رو حل
% میکنه.
% TODO: جلسه بعد