### 2024-12-14 system-evaluation/project/rip.tex
wip: add draft of project

\documentclass[a4paper]{article}
\usepackage{forest}
\usepackage{float}
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{color}
% \usepackage{xepersian}
\usepackage{subfiles}
\newgeometry{left=1.4cm, right=1.4cm, bottom=2.0cm, top=2.0cm}
% \settextfont[Scale=1]{XB Roya}
\input{../config.tex}

\title{RIP Project Report}
\author{Alireza Soltani Neshan}

\begin{document}
\maketitle

\section{Pre-requirements}

\begin{itemize}
    \item \texttt{PPP\_DS3} link has a data rate of 44.736 Mbps. All the routers
    connected with this link.
    \item RIP traffic is the total amount of RIP update traffic (in bits)
    sent\/received per second by all the nodes using RIP as the routing protocol
    in the IP interfaces in the node.
    \item Update list of files and the model directories with \textbf{File},
    \textbf{Manage Model Files} and \textbf{Refresh Model Directories}.
\end{itemize}

\subsection{Print out the layout of the network I implemented in this lab}

\begin{lstlisting}
# 
# Purpose:   Contains IP address information for all active 
#            interfaces in the current network model.
#            (created by exporting this information from the model.)
#

# Node Name: Campus Network.router_1
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.0.1        255.255.255.0    Campus Network.net_10 <-> router_1
   IF1                      192.0.1.1        255.255.255.0    Campus Network.net_11 <-> router_1
   IF10                     192.0.2.1        255.255.255.0    Campus Network.router_2 <-> router_1
   IF11                     192.0.3.1        255.255.255.0    Campus Network.router_1 <-> router_3

# Node Name: Campus Network.net_10
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.0.2        255.255.255.0    Campus Network.net_10 <-> router_1

# Node Name: Campus Network.net_11
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.1.2        255.255.255.0    Campus Network.net_11 <-> router_1

# Node Name: Campus Network.router_2
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.4.1        255.255.255.0    Campus Network.net_12 <-> router_2
   IF1                      192.0.5.1        255.255.255.0    Campus Network.net_13 <-> router_2
   IF10                     192.0.2.2        255.255.255.0    Campus Network.router_2 <-> router_1
   IF11                     192.0.6.1        255.255.255.0    Campus Network.router_4 <-> router_2

# Node Name: Campus Network.net_12
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.4.2        255.255.255.0    Campus Network.net_12 <-> router_2

# Node Name: Campus Network.net_13
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.5.2        255.255.255.0    Campus Network.net_13 <-> router_2

# Node Name: Campus Network.router_3
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.7.1        255.255.255.0    Campus Network.net_14 <-> router_3
   IF1                      192.0.8.1        255.255.255.0    Campus Network.net_15 <-> router_3
   IF10                     192.0.3.2        255.255.255.0    Campus Network.router_1 <-> router_3
   IF11                     192.0.9.1        255.255.255.0    Campus Network.router_3 <-> router_4

# Node Name: Campus Network.net_14
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.7.2        255.255.255.0    Campus Network.net_14 <-> router_3

# Node Name: Campus Network.net_15
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.8.2        255.255.255.0    Campus Network.net_15 <-> router_3

# Node Name: Campus Network.router_4
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.10.1       255.255.255.0    Campus Network.net_16 <-> router_4
   IF1                      192.0.11.1       255.255.255.0    Campus Network.net_17 <-> router_4
   IF10                     192.0.9.2        255.255.255.0    Campus Network.router_3 <-> router_4
   IF11                     192.0.6.2        255.255.255.0    Campus Network.router_4 <-> router_2

# Node Name: Campus Network.net_16
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.10.2       255.255.255.0    Campus Network.net_16 <-> router_4

# Node Name: Campus Network.net_17
#  Iface Name            IP Address       Subnet Mask      Connected Link
#  ----------            ---------------  ---------------  ----------------
   IF0                      192.0.11.2       255.255.255.0    Campus Network.net_17 <-> router_4
\end{lstlisting}

\end{document}